### 2019-03-04 report/final-report.tex
added refs to optician, a few more acronyms

The products of this investigation include several published
papers~\cite{bijective-synthesis, quotient-synthesis, symmetric-synthesis}
describing and evaluating our algorithms, as well as open-source 
code~\cite{GitHub} that implements those algorithms.  In this report,
we summarize our key methods, results, and findings, focusing
on the core algorithms for bijective synthesis, quotient synthesis, and
simple symmetric synthesis.

@@

We have written
papers~\cite{bijective-synthesis,quotient-synthesis,symmetric-synthesis}
describing and evaluating our algorithms and produced open-source 
code~\cite{GitHub} that implements those algorithms.  In this report,
we summarize some of our key methods, results and findings, focusing
on the core algorithms for bijective synthesis and quotient synthesis.

@@

\section{List of Symbols, Abbreviations, and Acronyms}
\begin{tabular}{p{1in}p{5in}}
  \ToDNFRegex{}         & An operation that converts regular   expressions into DNF form\\
  \ToLens{}             & An operation that converts a DNF lens to a
  lens \\
  $\equiv_S$, $\equiv_T$ & Equivalence relations on data matching
                           regular expressions $S$ and $T$
                           respectively \\
  \AnyOpt{}             & Mode for simple symmetric synthesis that ignores the information-theoretic metric \\ 
  AST     & Abstract syntax tree\\  
  \BSOpt{}              & Bijective lens synthesis algorithm\\
  DARPA   & Defense Advanced Research Project Agency \\
  \CCOpt{}              & Mode for simple symmetric synthesis that
                          replace our information-theoretic cost metric with one where 
                          the cost of the lens is the number of disconnects plus the number
                          of merges.\\
  \DNFLens{}            & Lens in disjunctive normal form\\
  DNF                   & Disjunctive normal form\\
  \DNFRegex{}, \DNFRegexAlt{}  & Regular expression in disjunctive normal form\\
  \Examples{}           & Examples \\
  \Expand       & A component of the synthesis algorithm that proposes candidate
                  types equivalent to the input \\
  \FLOpt{}              & Mode for simple symmetric synthesis that
                          returns the first highest ranked lens found
                          by  \GreedySynth \\
  \GreedySynth & Synthesis procedure that searches greedily for candidate
                 solutions \\
  HR & Human Resources \\
  HTML & Hyptertext Markup Language \\
  JSON & JavaScript Object Notation---a standard file format used to
         encode data objects\\
  \Lens{}               & A lens \\
  \NROpt{}              & Mode for simple symmetric synthesis that
                          ignores all \SRequire annotations in the SRE specifications. \\
  \NSOpt{}              & Mode for simple symmetric syntehsis that
                          ignores all \Skip annotations in the SRE specifications. \\ 
  QRE                   & Quotient regular expression\\
  \textbf{QS}  & Number of nodes in the abstract syntax of QRE specifications \\
  RDF & Resource Description Framework---used to model web resources \\
  REST & Representational State Transfer\\
  SRE                   & Stochastic regular expression\\
  \BRegex and \BRegexAlt & Regular expressions provided by the user\\
  \Regex{}, \RegexAlt{} & Regular expressions\\
  $S \Leftrightarrow T$ & Type of a lens that maps between data
                          described by regular expressions $S$ and $T$\\
  \SSOpt{}              & Full symmetric synthesis algorithm\\
  \SSNCOpt{}            & Symmetric synthesis algorithm without using a library of
    existing lenses.\\
  XML & Extensible Markup Language---used in web services \\
\end{tabular}

>>>>

The products of this investigation include several published
papers~\cite{bijective-synthesis, quotient-synthesis, symmetric-synthesis}
describing and evaluating our algorithms, as well as open-source 
code~\cite{GitHub} that implements those algorithms in (several variants of) a
prototype tool called \Optician{}.  In this report,
we summarize our key methods, results, and findings, focusing
on the core algorithms for bijective synthesis, quotient synthesis, and
simple symmetric synthesis.

@@

We have written
papers~\cite{bijective-synthesis,quotient-synthesis,symmetric-synthesis}
describing and evaluating our algorithms and produced open-source
code~\cite{GitHub} that implements those algorithms in (several variants of) a
tool called \Optician{}.  In this report, we summarize some of our key methods,
results and findings, focusing on the core algorithms for bijective synthesis
and quotient synthesis.

@@

\section{List of Symbols, Abbreviations, and Acronyms}
\begin{tabular}{p{1in}p{5in}}
  \ToDNFRegex{}         & An operation that converts regular   expressions into DNF form\\
  \ToLens{}             & An operation that converts a DNF lens to a  lens \\
  $\equiv_S$, $\equiv_T$ & Equivalence relations on data matching
                           regular expressions $S$ and $T$
                           respectively \\
  \AnyOpt{}             & Mode for simple symmetric synthesis that ignores the information-theoretic metric \\ 
  AST     & Abstract syntax tree\\  
  \BSOpt{}              & Bijective lens synthesis algorithm\\
  DARPA   & Defense Advanced Research Project Agency \\
  \CCOpt{}              & Mode for simple symmetric synthesis that
                          replace our information-theoretic cost metric with one where 
                          the cost of the lens is the number of disconnects plus the number
                          of merges.\\
  \DNFLens{}            & Lens in disjunctive normal form\\
  DNF                   & Disjunctive normal form\\
  \DNFRegex{}, \DNFRegexAlt{}  & Regular expression in disjunctive normal form\\
  \Examples{}           & Examples \\
  \Expand       & A component of the synthesis algorithm that proposes candidate
                  types equivalent to the input \\
  \FLOpt{}              & Mode for simple symmetric synthesis that
                          returns the first highest ranked lens found
                          by  \GreedySynth \\
  \GreedySynth & Synthesis procedure that searches greedily for candidate
                 solutions \\
  HR & Human Resources \\
  HTML & Hyptertext Markup Language \\
  JSON & JavaScript Object Notation---a standard file format used to
         encode data objects\\
  \Lens{}               & A lens \\
  $\mathcal{L}(\BRegex{})$  & The language of strings for the regular expression
                             \BRegex{} \\
  \NROpt{}              & Mode for simple symmetric synthesis that
                          ignores all \SRequire annotations in the SRE specifications. \\
  \NSOpt{}              & Mode for simple symmetric syntehsis that
                          ignores all \Skip annotations in the SRE specifications. \\ 
  QRE                   & Quotient regular expression\\
  \textbf{QS}  & Number of nodes in the abstract syntax of QRE specifications \\
  RDF & Resource Description Framework---used to model web resources \\
  REST & Representational State Transfer\\
  SRE                   & Stochastic regular expression\\
  \BRegex and \BRegexAlt & Regular expressions provided by the user\\
  \Regex{}, \RegexAlt{} & Regular expressions\\
  $S \Leftrightarrow T$ & Type of a lens that maps between data
                          described by regular expressions $S$ and $T$\\
  \SSOpt{}              & Full symmetric synthesis algorithm\\
  \SSNCOpt{}            & Symmetric synthesis algorithm without using a library of
    existing lenses.\\
  XML & Extensible Markup Language---used in web services \\
\end{tabular}
